LAGOS lake depth

### 2020-04-13 figures/01_hypsography.Rmd
include class breakdown in hypso fig

ids <- factor(c("convex", "concave"))
polys <- data.frame(
  id = rep(ids, each = 3),
  x = c(0, 100, 0, 
        0, 100, 100), 
  y = c(100, 0, 0, 
        100, 100, 0))

@@

ggplot(data = dt_raw) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = llid)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") + 
  ggtitle(paste0("Normalized hypsography for ", length(unique(dt_raw$llid)), " lakes")) + 
  theme(legend.position = c(0.84, 0.2), 
        legend.title = element_blank()) +
  facet_wrap(~state)

>>>>

ids <- factor(c("convex", "concave"), levels = c("convex", "concave"))
polys <- data.frame(
  id = rep(ids, each = 3),
  x = c(0, 100, 0, 
        0, 100, 100), 
  y = c(100, 0, 0, 
        100, 100, 0))

@@

# generate labels with percent in each class
dt_classes <- read.csv("../data/00_hypso/hypso_classes.csv", 
                       stringsAsFactors = FALSE) %>%
  left_join(dt_raw)
class_tally <- dt_classes %>%
  dplyr::filter(shape_class != "neither") %>%
  group_by (state, shape_class) %>%
  summarise (n=n()) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 0), "%")) %>%
  dplyr::select(-n) %>%
  tidyr::pivot_wider(names_from = state, values_from = rel.freq) %>%
  t()
class_tally <- setNames(
  tibble::as_tibble(class_tally[-1,]), c("concave", "convex")) %>%
  mutate(state = row.names(class_tally)[-1]) %>%
  mutate(state_label = paste0(state, " (", convex, ",", concave, ")"))
dt_raw <- left_join(dt_raw, class_tally, by = "state")

res <- ggplot(data = dt_raw) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.5) +
  scale_fill_manual(values = c(concave = "#F8766D", convex = "#00BA38")) +
  geom_line(aes(x = area_percent, y = depth_percent, group = llid), size = 0.2) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") + 
  ggtitle(paste0("Normalized hypsography for ", length(unique(dt_raw$llid)), " lakes")) + 
  theme(legend.position = c(0.84, 0.2), 
        legend.title = element_blank()) +
  facet_wrap(~state_label)

leg <- cowplot::get_legend(res + theme(legend.direction = "horizontal"))

cowplot::plot_grid(res + theme(legend.position = "none"), 
                   leg, 
                   nrow = 2, rel_heights = c(1, 0.09))
